---
title: "p8105_hw5_mff2137"
author: "Mohammad Fouda"
output: github_document
---


```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2

### Read in the data 

First, we read in the `homicide-data` and create a `city-state` variable

```{r}
homicide <-
  read_csv("data/homicide-data.csv") %>% 
  mutate(city_state = str_c(city, ", ", state)) 
```

### Description

The `homicide` dataset has data on criminal homicides over a decade in 50 of the largest American cities with each row representing a homicide. It has `r ncol(homicide)` variables and `r nrow(homicide)` observations. Variables include identifier of each homicide, date reported, victim information (name, sex, race, age), the city and state where it happened, specific coordinates of the incident, and the disposition of each case (e.g. closed by arrest, closed without arrest, open/no arrest).

### Data wrangling

In this step, we summarize across cities to obtain the total number of homicides and the an the number of unsolved homicides. The total number of homicides in Baltimore, MD is 2827.


```{r}
balt_total <-
  homicide %>% 
  filter(city_state == "Baltimore, MD") %>% 
  group_by(city_state) %>% 
  summarize(total = n()) 
```

To obtain the number of unsolved homicides, we summarize by `city-state` and `disposition`, then combine the number of homicides of which disposition is “Closed without arrest” or “Open/No arrest”. The number of unsolved homicides in Baltiomre, MD is 1825

```{r}
balt_open <-
  homicide %>% 
  filter(city_state == "Baltimore, MD", disposition %in% c("Closed without arrest", "Open/No arrest")) %>%
  group_by(city_state) %>% 
  summarize(unresolved = n()) 
```

This step produces a data frame with counts of both unresolved and total homicides in Baltimore 

```{r}
balt_df <-
  inner_join(balt_open, balt_total)

balt_df
```

The same approach could be used to tidy the `homicide` dataframe to prepare it for running the `prop.test` on all 50 cities included in the dataset.

```{r}
homicide_open <-
  homicide %>% 
  filter( disposition %in% c("Closed without arrest", "Open/No arrest")) %>%
  group_by(city_state) %>% 
  summarize(unresolved = n())

homicide_total <-
  homicide %>% 
  group_by(city_state) %>% 
  summarize(total = n())

homicide_df <-
  inner_join(homicide_open, homicide_total)
```


### Baltimore `prop.test` function

In this step, we create a function to compute the `prop.test` function in order to estimate the proportion of homicides that are unresolved in Baltiomore, MD. Using `purr::map` function. The estimate is 0.646 and the 95% confidence interval is 0.628, 0.663. These results are saved to a tidy dataframe `balt_prop`. 


```{r}
prop_test = function(df) {
  
  prop.test(
    x = df %>% pull(unresolved),
    n = df %>% pull(total),
    alternative = c("t"),
    conf.level = 0.95, correct = TRUE) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf"))
}

balt_prop <- prop_test(balt_df)
```

### Applying the function across cities 

Using `purr::map2` function, we run the `prop.test` for each of the cities in the `homicide` dataset, then extract both the proportion of unsolved homicides and the confidence interval for each, saving the results in a list column. Next, we unnest as to create a tidy dataframe with results.

```{r}
homicide_prop_df <-
  homicide_df %>%
  mutate(
    prop_results = map2(.x = unresolved, .y = total, ~ prop.test(x = .x, n = .y)  %>% 
  broom::tidy())) %>% 
  unnest() %>% 
  select(city_state, estimate, starts_with("conf"))
```

