---
title: "p8105_hw5_mff2137"
author: "Mohammad Fouda"
output: github_document
---


```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2

### Read in the data 

First, we read in the `homicide-data` and create a `city-state` variable

```{r}
homicide <-
  read_csv("data/homicide-data.csv") %>% 
  mutate(city_state = str_c(city, ", ", state)) 
```

### Description

The `homicide` dataset has data on criminal homicides over a decade in 50 of the largest American cities with each row representing a homicide. It has `r ncol(homicide)` variables and `r nrow(homicide)` observations. Variables include identifier of each homicide, date reported, victim information (name, sex, race, age), the city and state where it happened, specific coordinates of the incident, and the disposition of each case (e.g. closed by arrest, closed without arrest, open/no arrest).

### Clean and tidy data

In this step, we summarize across cities to obtain the total number of homicides and the an the number of unsolved homicides (with disposition. The total number of homicides in Baltimore, MD is 2827.

```{r}
hom_total <-
  homicide %>% 
  group_by(city_state) %>% 
  count()
```

To obtain the number of unsolved homicides, we summarize by `city-state` and `disposition`, then combine the number of homicides of which disposition is “Closed without arrest” or “Open/No arrest”). The number of unsolved homicides in Baltiomre, MD is 1825

```{r}
hom_disp <-
  homicide %>% 
  group_by(city_state, disposition) %>% 
  count()
```

