---
title: "p8105_hw5_mff2137"
author: "Mohammad Fouda"
output: github_document
---


```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2

### Read in the data 

First, we read in the `homicide-data` and create a `city-state` variable

```{r}
homicide <-
  read_csv("data/homicide-data.csv") %>% 
  mutate(city_state = str_c(city, ", ", state)) 
```

### Description

The `homicide` dataset has data on criminal homicides over a decade in 50 of the largest American cities with each row representing a homicide. It has `r ncol(homicide)` variables and `r nrow(homicide)` observations. Variables include identifier of each homicide, date reported, victim information (name, sex, race, age), the city and state where it happened, specific coordinates of the incident, and the disposition of each case (e.g. closed by arrest, closed without arrest, open/no arrest).

### Clean and tidy data

In this step, we summarize across cities to obtain the total number of homicides and the an the number of unsolved homicides. The total number of homicides in Baltimore, MD is 2827.


```{r}
balt_total <-
  homicide %>% 
  filter(city_state == "Baltimore, MD") %>% 
  group_by(city_state) %>% 
  summarize(total = n()) 
```

To obtain the number of unsolved homicides, we summarize by `city-state` and `disposition`, then combine the number of homicides of which disposition is “Closed without arrest” or “Open/No arrest”. The number of unsolved homicides in Baltiomre, MD is 1825

```{r}
balt_open <-
  homicide %>% 
  filter(city_state == "Baltimore, MD", disposition %in% c("Closed without arrest", "Open/No arrest")) %>%
  group_by(city_state) %>% 
  summarize(unresolved = n()) 
```

This step produces a data frame with counts of both unresolved and total homicides in Baltimore 

```{r}
balt_df <-
  inner_join(balt_open, balt_total)
```

## Baltimore `prop.test`

To estimate the proportion of unresolved homicides in Baltimore, MD, we use the `prop.test` . The resulting proportion is 0.646 and the 95% confidence interval is 0.628, 0.663

```{r}
balt_test <-
  prop.test(1825, 2827) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf"))

balt_test
```

Another way, same result...

```{r}
prop_balt <-
  prop.test(
    x = balt_df %>% pull(unresolved),
    n = balt_df %>% pull(total),
    alternative = c("t"),
    conf.level = 0.95, correct = TRUE) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf"))

prop_balt
```





